Modelling the emergence of whisker barrels

### 2020-07-02 paper/briefpaper/brief.tex
Correction to caption for the average neighbour barrel area

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig4.png}
  \captionof{figure}{
    \MPthreePred{
      Two simulated whisker barrel manipulations.  Guidance fields
      (\textbf{A}) and emergent barrel pattern (\textbf{B}) in a Fgf8
      misexpression experiment
      (c.f.~\citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
      $\rho_1$ from Fig.\,\ref{fig:main}A at the join of the original boundary
      with its mirror. The model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{C} Simulating whisker trimming by a
      reduction of the competition parameter, $\epsilon$, in the expression
      $\chi_i$ (Eq.\,\ref{eq:comp}) for the C3 thalamocortical projection. For
      C3, $\epsilon$ is replaced by $m\,\epsilon$, where $m$ is a scalar
      multiplier. For the rest of the projections, $\chi_i$ is left unchanged
      and all other parameters are identical to those reported in
      Fig.\,\ref{fig:main}C. The pattern formed after 30000 steps with
      $m=0.64$. Barrel C3 is reduced in size as its axon branching competes
      less strongly with its neighbours, whose area is slightly
      increased. \textbf{D} Individual barrel area plotted vs.~$m$ shows that
      as $m$ is reduced, the area of C3 (blue squares) goes down, disappearing
      for $m\approx0.5$, whereas the average area of neighbouring barrels
      (triangles) increases. Scale bars are 1\,mm.
    }
  }
  \label{fig:fgf8}
\end{center}

>>>>

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig4.png}
  \captionof{figure}{
    \MPthreePred{
      Two simulated whisker barrel manipulations.  Guidance fields
      (\textbf{A}) and emergent barrel pattern (\textbf{B}) in a Fgf8
      misexpression experiment
      (c.f.~\citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
      $\rho_1$ from Fig.\,\ref{fig:main}A at the join of the original boundary
      with its mirror. The model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{C} Simulating whisker trimming by a
      reduction of the competition parameter, $\epsilon$, in the expression
      $\chi_i$ (Eq.\,\ref{eq:comp}) for the C3 thalamocortical projection. For
      C3, $\epsilon$ is replaced by $m\,\epsilon$, where $m$ is a scalar
      multiplier. For the rest of the projections, $\chi_i$ is left unchanged
      and all other parameters are identical to those reported in
      Fig.\,\ref{fig:main}C. The pattern formed after 30000 steps with
      $m=0.64$. Barrel C3 is reduced in size as its axon branching competes
      less strongly with its neighbours, whose area is slightly
      increased. \textbf{D} Individual barrel area plotted vs.~$m$ for C3
      (black squares) shows that
      as $m$ is reduced, its area goes down, disappearing
      for $m\approx0.5$, whereas the mean area of neighbouring barrels
      B3, C2, C4, D2 \& D3
      (grey circles) increases. Scale bars are 1\,mm.
    }
  }
  \label{fig:fgf8}
\end{center}
